Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings_SI.Rmd
remove SI figures, update fig numbers (now matches manuscript)
#130

#SI figure numbers
all_recruitment_plots="S1-S10"

all_traditional_comparisons = "S11-S14"
SCBI_traditional_comparison = "S11"
Zofin_traditional_comparison = "S12"
CB_traditional_comparison = "S13"
SC_traditional_comparison = "S14"

all_climwin = "S15-S34"
climwin_BCNM_W = "S15"
climwin_BCNM_T = "S16"
climwin_HKK_W = "S17"
climwin_HKK_T = "S18"
climwin_SCBI_W = "S19"
climwin_SCBI_T = "S20"

all_GLS = "S35-S54"
GLS_BCNM = "S35"
GLS_BCNM_year = "S36"
GLS_HKK = "S37"
GLS_HKK_year = "S38"
GLS_SCBI = "S39"
GLS_SCBI_year = "S40"
GLS_LDW = "S41"
GLS_LDW_year = "S42"
GLS_HF = "S43"
GLS_HF_year = "S44"
GLS_ZOF = "S45"
GLS_ZOF_year = "S46"
GLS_NIO = "S47"
GLS_NIO_year = "S48"
GLS_LT = "S49"
GLS_LT_year = "S50"
GLS_CB = "S51"
GLS_CB_year = "S52"
GLS_SC = "S53"
GLS_SC_year = "S54"

SC_1970break = "S55"

RW_interactions_all= "S56"
BAI_interactions_all= "S57"

decadal_analysis_figs_all = "S58-S67"
decadal_plot_BCNM = "S58"
decadal_plot_HKK = "S59"
decadal_plot_SCBI = "S60"
decadal_plot_LDW = "S61"
decadal_plot_HF = "S62"
decadal_plot_ZOF = "S63"
decadal_plot_NIO = "S64"
decadal_plot_LT = "S65"
decadal_plot_CB = "S66"
decadal_plot_SC = "S67"

#SI figure captions
recruitment_plot_BCNM_legend = "Figure S1. Density plot of core record start years by species for BCNM."
recruitment_plot_HKK_legend = "Figure S2. Density plot of core record start years by species for HKK."
recruitment_plot_SCBI_legend = "Figure S3. Density plot of core record start years by species for SCBI."
recruitment_plot_LDW_legend = "Figure S4. Density plot of core record start years by species for LDW."
recruitment_plot_HF_legend = "Figure S5. Density plot of core record start years by species for HF."
recruitment_plot_ZOF_legend = "Figure S6. Density plot of core record start years by species for ZOF."
recruitment_plot_NIO_legend = "Figure S7. Density plot of core record start years by species for NIO."
recruitment_plot_LT_legend = "Figure S8. Density plot of core record start years by species for LT."
recruitment_plot_CB_legend = "Figure S9. Density plot of core record start years by species for CB."
recruitment_plot_SC_legend = "Figure S10. Density plot of core record start years by species for SC."

SCBI_traditional_comparison_legend <- "Figure S11. Comparison of our approach with traditional methods of identifying climate signals: *Liriodendron tulipifera* at SCBI."
Zofin_traditional_comparison_legend <- "Figure S12. Comparison of our approach with traditional methods of identifying climate signals: *Abies alba* at Zofin."
CB_traditional_comparison_legend <- "Figure S13. Comparison of our approach with traditional methods of identifying climate signals: *Pseudotsuga menziesii* at Cedar Breaks."
SC_traditional_comparison_legend <- "Figure S14. Comparison of our approach with traditional methods of identifying climate signals: *Picea mariana* at Scotty Creek."

climwin_BCNM_W_legend = "Figure S15. Climwin output for water variable group at BCNM."
climwin_BCNM_T_legend = "Figure S16. Climwin output for temperature variable group at BCNM."
climwin_HKK_W_legend =  "Figure S17. Climwin output for water variable group at HKK."
climwin_HKK_T_legend = "Figure S18. Climwin output for temperature variable group at HKK."
climwin_SCBI_W_legend  = "Figure S19. Climwin output for water variable group at SCBI."
climwin_SCBI_T_legend = "Figure S20. Climwin output for temperature variable group at SCBI."
climwin_LDW_W_legend = "Figure S21. Climwin output for water variable group at LDW."
climwin_LDW_T_legend = "Figure S22. Climwin output for temperature variable group at LDW."
climwin_HF_W_legend =  "Figure S23. Climwin output for water variable group at HF."
climwin_HF_T_legend = "Figure S24. Climwin output for temperature variable group at HF."
climwin_ZOF_W_legend  = "Figure S25. Climwin output for water variable group at ZOF."
climwin_ZOF_T_legend = "Figure S26. Climwin output for temperature variable group at ZOF."
climwin_NIO_W_legend = "Figure S27. Climwin output for water variable group at NIO."
climwin_NIO_T_legend = "Figure S28. Climwin output for temperature variable group at NIO."
climwin_LT_W_legend =  "Figure S29. Climwin output for water variable group at LT."
climwin_LT_T_legend = "Figure S30. Climwin output for temperature variable group at LT."
climwin_CB_W_legend  = "Figure S31. Climwin output for water variable group at CB."
climwin_CB_T_legend = "Figure S32. Climwin output for temperature variable group at CB."
climwin_SC_W_legend  = "Figure S33. Climwin output for water variable group at SC."
climwin_SC_T_legend = "Figure S34. Climwin output for temperature variable group at SC."

GLS_BCNM_legend = "Figure S35. Best GLS models including climate and DBH for BCNM"
GLS_BCNM_year_legend = "Figure S36. Best GLS models including climate, DBH, and year for BCNM"
GLS_HKK_legend = "Figure S37. Best GLS models including climate and DBH for HKK"
GLS_HKK_year_legend = "Figure S38. Best GLS models including climate, DBH, and year for HKK"
GLS_SCBI_legend = "Figure S39. Best GLS models including climate and DBH for SCBI"
GLS_SCBI_year_legend = "Figure S40. Best GLS models including climate, DBH, and year for SCBI"
GLS_LDW_legend = "Figure S41. Best GLS models including climate and DBH for LDW"
GLS_LDW_year_legend = "Figure S42. Best GLS models including climate, DBH, and year for LDW"
GLS_HF_legend = "Figure S43. Best GLS models including climate and DBH for HF"
GLS_HF_year_legend = "Figure S44. Best GLS models including climate, DBH, and year for HF "
GLS_ZOF_legend = "Figure S45. Best GLS models including climate and DBH for ZOF"
GLS_ZOF_year_legend = "Figure S46. Best GLS models including climate, DBH, and year for ZOF"
GLS_NIO_legend = "Figure S47. Best GLS models including climate and DBH for NIO"
GLS_NIO_year_legend = "Figure S48. Best GLS models including climate, DBH, and year for NIO"
GLS_LT_legend = "Figure S49. Best GLS models including climate and DBH for LT"
GLS_LT_year_legend = "Figure S50. Best GLS models including climate, DBH, and year for LT"
GLS_CB_legend = "Figure S51. Best GLS models including climate and DBH for CB"
GLS_CB_year_legend = "Figure S52. Best GLS models including climate, DBH, and year for CB"
GLS_SC_legend = "Figure S53. Best GLS models including climate and DBH for SC"
GLS_SC_year_legend = "Figure S54. Best GLS models including climate, DBH, and year for SC"

SC_1970break_legend = "Figure S55. Climate responses at SC before and after 1970."

RW_interactions_all_legend = "Figure S56. All significant climate - DBH interactions with RW as the response metric."
BAI_interactions_all_legend ="Figure S57. All significant climate - DBH interactions with BAI as the response metric."

decadal_plot_BCNM_legend = "Figure S58. Relationships between DBH and BAI by decade for BCNM."
decadal_plot_HKK_legend = "Figure S59. Relationships between DBH and BAI by decade for HKK."
decadal_plot_SCBI_legend = "Figure S60. Relationships between DBH and BAI by decade for SCBI."
decadal_plot_LDW_legend = "Figure S61. Relationships between DBH and BAI by decade for LDW."
decadal_plot_HF_legend = "Figure S62. Relationships between DBH and BAI by decade for HF."
decadal_plot_ZOF_legend = "Figure S63. Relationships between DBH and BAI by decade for ZOF."
decadal_plot_NIO_legend = "Figure S64. Relationships between DBH and BAI by decade for NIO."
decadal_plot_LT_legend = "Figure S65. Relationships between DBH and BAI by decade for LT."
decadal_plot_CB_legend = "Figure S66. Relationships between DBH and BAI by decade for CB."
decadal_plot_SC_legend = "Figure S67. Relationships between DBH and BAI by decade for SC."

@@

recruitment_generic_legend = "This distribution approximates -- but does not entirely match -- the age distribution of trees cored. The core record start year can occur after a tree's recruitment year (i.e., year when the tree reached coring height) if the core fails to hit center or if the tree's center is lost to heartrot."

@@

decadal_generic_legend = "Plot visualizes the data included in the GLS model, separated by decade, using a probability density function. Transparent ribbons indicate 95% confidence intervals."
```

@@

\newpage
## `r climwin_BCNM_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/BCI_pre.png)

`r climwin_BCNM_W_legend` `r climwin_generic`

\newpage
## `r climwin_BCNM_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/BCI_tmn.png)

`r climwin_BCNM_T_legend` `r climwin_generic`

\newpage
## `r climwin_HKK_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HKK_wet.png)

`r climwin_HKK_W_legend` `r climwin_generic`

@@

\newpage
## `r climwin_LDW_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/LillyDickey_pre.png)

`r climwin_LDW_W_legend` `r climwin_generic`

\newpage
## `r climwin_LDW_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/LillyDickey_pet.png)

`r climwin_LDW_T_legend` `r climwin_generic`

@@

\newpage
## `r climwin_HF_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HarvardForest_pet.png)

`r climwin_HF_T_legend` `r climwin_generic`

\newpage
## `r climwin_ZOF_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Zofin_wet.png)

`r climwin_ZOF_W_legend` `r climwin_generic`

\newpage
## `r climwin_ZOF_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Zofin_tmx.png)

`r climwin_ZOF_T_legend` `r climwin_generic`

\newpage
## `r climwin_NIO_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Niobara_pre.png)

`r climwin_NIO_W_legend` `r climwin_generic`

\newpage
## `r climwin_NIO_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Niobara_tmx.png)

`r climwin_NIO_T_legend` `r climwin_generic`

\newpage
## `r climwin_LT_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/NewMexico_pre.png)

`r climwin_LT_W_legend` `r climwin_generic`

\newpage
## `r climwin_LT_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/NewMexico_tmx.png)

`r climwin_LT_T_legend` `r climwin_generic`

\newpage
## `r climwin_CB_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/CedarBreaks_pre.png)

`r climwin_CB_W_legend` `r climwin_generic`

\newpage
## `r climwin_CB_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/CedarBreaks_tmx.png)

`r climwin_CB_T_legend` `r climwin_generic`

\newpage
## `r climwin_SC_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/ScottyCreek_pre.png)

`r climwin_SC_W_legend` `r climwin_generic`

\newpage
## `r climwin_SC_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/ScottyCreek_tmx.png)

`r climwin_SC_T_legend` `r climwin_generic`

@@

\newpage
## `r GLS_BCNM_year_legend`

![`r GLS_BCNM_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI_with_Year.png){ width=90% }

\newpage
## `r GLS_HKK_legend`

![`r GLS_HKK_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HKK.png){ width=90% }

\newpage
## `r GLS_HKK_year_legend`

![`r GLS_HKK_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HKK_with_Year.png){ width=90% }

@@

\newpage
## `r GLS_LDW_legend`

![`r GLS_LDW_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/LillyDickey.png){ width=90% }

\newpage
## `r GLS_LDW_year_legend`

![`r GLS_LDW_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/LillyDickey_with_Year.png){ width=90% }

\newpage
## `r GLS_HF_legend`

![`r GLS_HF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HarvardForest.png){ width=90% }

\newpage
## `r GLS_HF_year_legend`

![`r GLS_HF_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HarvardForest_with_Year.png){ width=90% }

\newpage
## `r GLS_ZOF_legend`

![`r GLS_ZOF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Zofin.png){ width=90% }

\newpage
## `r GLS_ZOF_year_legend`

![`r GLS_ZOF_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Zofin_with_Year.png){ width=90% }

\newpage
## `r GLS_NIO_legend`

![`r GLS_NIO_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Niobara.png){ width=90% }

\newpage
## `r GLS_NIO_year_legend`

![`r GLS_NIO_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Niobara_with_Year.png){ width=90% }

@@

\newpage
## `r GLS_LT_year_legend`

![`r GLS_LT_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico_with_Year.png){ width=90% }

\newpage
## `r GLS_CB_legend`

![`r GLS_CB_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/CedarBreaks.png){ width=90% }

\newpage
## `r GLS_CB_year_legend`

![`r GLS_CB_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/CedarBreaks_with_Year.png){ width=90% }

\newpage
## `r GLS_SC_legend`

![`r GLS_SC_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/ScottyCreek.png){ width=90% }

\newpage
## `r GLS_SC_year_legend`

![`r GLS_SC_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/ScottyCreek_with_Year.png){ width=90% }

@@

\newpage
## `r BAI_interactions_all_legend`

![`r BAI_interactions_all_legend` Shown are modeled response functions at the minimum and maximum and maximum ends of the DBH range. Other terms in the model are held constant at their median. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver, shading indicates 1 SD.](tables_figures/pre_temp_groups_dbh_interactions_log_BAI_dbh.png){ width=90% }

>>>>

#SI figure numbers
##traditional comparisons
all_traditional_comparisons = "S1-S4"
SCBI_traditional_comparison = "S1"
Zofin_traditional_comparison = "S2"
CB_traditional_comparison = "S3"
SC_traditional_comparison = "S4"

decadal_analysis_verification_example = "S5"

##climwin
climwin_HKK_T = "S6"
climwin_SCBI_W = "S7"
climwin_SCBI_T = "S8"
climwin_HF_W = "S9"

##GLS
GLS_BCNM = "S10"
GLS_SCBI = "S11"
GLS_SCBI_year = "S12"
GLS_LT = "S13"

SC_1970break = "S14"

RW_interactions_all= "S15"

#SI figure captions

SCBI_traditional_comparison_legend <- "Figure S1. Comparison of our approach with traditional methods of identifying climate signals: *Liriodendron tulipifera* at SCBI."
Zofin_traditional_comparison_legend <- "Figure S1. Comparison of our approach with traditional methods of identifying climate signals: *Abies alba* at Zofin."
CB_traditional_comparison_legend <- "Figure S3. Comparison of our approach with traditional methods of identifying climate signals: *Pseudotsuga menziesii* at Cedar Breaks."
SC_traditional_comparison_legend <- "Figure S4. Comparison of our approach with traditional methods of identifying climate signals: *Picea mariana* at Scotty Creek."

decadal_analysis_verification_example_legend <- "Figure S5. Example comparison of year effect in GLS model with independent decadal analysis: BCNM"

climwin_HKK_T_legend = "Figure S6. Climwin output for temperature variable group at HKK."
climwin_SCBI_W_legend  = "Figure S7. Climwin output for water variable group at SCBI."
climwin_SCBI_T_legend = "Figure S8. Climwin output for temperature variable group at SCBI."
climwin_HF_W_legend =  "Figure S9. Climwin output for water variable group at HF."

GLS_BCNM_legend = "Figure S10. Best GLS models including climate and DBH for BCNM"
GLS_SCBI_legend = "Figure S11. Best GLS models including climate and DBH for SCBI"
GLS_SCBI_year_legend = "Figure S12. Best GLS models including climate, DBH, and year for SCBI"
GLS_LT_legend = "Figure S13. Best GLS models including climate and DBH for LT"

SC_1970break_legend = "Figure S14. Climate responses at SC before and after 1970."

RW_interactions_all_legend = "Figure S15. All significant climate - DBH interactions with RW as the response metric."

@@

@@

```

@@

@@

@@

@@

@@

@@

@@
